---
title: " Biden Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill 
    theme: cerulean
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(janitor)
library(scales)
library(gt)
library(DT)
library(kableExtra)
library(htmlwidgets)
library(htmltools)
library(glue)
options(dplyr.summarise.inform = FALSE)
source("03_compare_current_with_previous.R")
```

Agency Review Teams Highlights
=====================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Current Additions to Agency Review Teams

```{r}
newnames <- anti_join(transition_data_current, transition_data_previous, by = "idstring")

newnames%>%
  knitr::kable() %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center", font_size = 12, fixed_thead = T) %>%
  row_spec(0, bold = T, color = "blue", font_size = 15) %>%
  column_spec(2, bold = T)


```

### Aggregate Team Changes

```{r}
agencycount_new = agencycount_current
just_change <- agencycount_compare %>% pull(change)
agencycount_new["change"] <- just_change

agencycount_new %>%
  filter(change > 0) %>%
knitr::kable() %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center", font_size = 12, fixed_thead = T) %>%
  row_spec(0, bold = T, color = "blue", font_size = 15) %>%
  column_spec(2, bold = T)
```


Column {data-width=350}
-----------------------------------------------------------------------

### Top 10 Largest Agency Review Teams

```{r}
agencycount_largest <- agencycount_current %>%
  arrange(desc(current_count)) %>%
  slice(1:10)

agencycount_largest %>%
   knitr::kable(caption = "Largest Agency Review Teams") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center", font_size = 12) %>%
  row_spec(0, bold = T, color = "blue", font_size = 15)
```

### Top 10 Smallest Agency Review Teams

```{r}
agencycount_smallest <- agencycount_current %>%
  arrange(current_count) %>%
  filter(current_count < 5)

agencycount_smallest %>%
   knitr::kable(caption = "Smallest Agency Review Teams") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center", font_size = 12) %>%
  row_spec(0, bold = T, color = "blue", font_size = 15)

```

White House Senior Staff Highlights
=====================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Newly Appointed Senior Staff

```{r}
newstaffnames <- anti_join(staff_data_current, staff_data_previous, by = "idstring")

newstaffnames %>%
  knitr::kable() %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center", font_size = 12, fixed_thead = T) %>%
  row_spec(0, bold = T, color = "blue", font_size = 15) %>%
  column_spec(1, bold = T)
```

### Total Number of Currently Named WH Staff vs. Previously Named WH Staff

```{r}
staff_count_previous <- c(nrow(staff_data_previous))
staff_count_current <- c(nrow(staff_data_current))                    
staff_data_compare <- data.frame(staff_count_previous, staff_count_current)

staff_data_compare %>%
  knitr::kable(caption = "Staff Count Comparison") %>%
  kable_classic() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "center", font_size = 12, fixed_thead = T) %>%
  row_spec(0, bold = T, color = "blue", font_size = 15) %>%
  column_spec(1:2, bold = T)

```

Agency Review Teams Database
=====================================================================
To filter, click on the boxes at the top of the columns. To sort, use the up/down arrows by the column names.

Column {data-width=650}
-----------------------------------------------------------------------

### Updated List of All Agency Review Teams

```{r}

datatable(agencyteams,
          rownames = FALSE,
          filter = "top",
          extensions = 'Buttons',
          options = list(searchHighlight = TRUE, bPaginate = FALSE, dom = 'Bfrtip',
       buttons = c('copy', 'csv', 'excel', 'print')
          ))

     
```





White House Senior Staff Database
=====================================================================
To filter, click on the boxes at the top of the columns. To sort, use the up/down arrows by the column names.

Column {data-width=650}
-----------------------------------------------------------------------

### Updated List of All White House Senior Staff

```{r}

datatable(whseniorstaff,
          rownames = FALSE,
          filter = "top",
          extensions = 'Buttons',
          options = list(searchHighlight = TRUE, bPaginate = FALSE, dom = 'Bfrtip',
       buttons = c('copy', 'csv', 'excel', 'print')
          ))

```


